Squint: Lossy Hierarchical Compression on Symbol Streams

### 2012-12-10 tex/paper.tex
tried to do a runtime analysis, more difficult to make fit data than I thought

\subsection{Mathematical Analysis}
Runtime Analysis
No-loops proof

@@

\begin{verbatim}
~[*] => ~[BC]--~[BC]?

~[AZ] => ~[A]3~[A]~[A] + ~[C]~[C]3~[C]1 = ???
~[A] => 12
~[BC] => ~[AZ]~[AZ]
~[C] => 32
-----------------------
1231212 + 32323321 = ???1231212 + 32323321 = ???--(cont.)
1231212 + 32323321 = ???1231212 + 32323321 = ????
\end{verbatim}

@@

\subsection{Larger Tests}
Final compression ratios on various benchmark data
ASCII ART =p
Our Code

>>>>

\subsection{Runtime Estimates}
Given an input of length $n$, let $r$ be the number of rules generated
by Sequitur from the input. Let $R$ be the total number of variable
replacements we perform. For each replacement, we had to have searched though
up to all pairs of variables, and for each pair of variables expanding
them and calculating the levenshtein distance could take time linear in $n$.
Thus the runtime is $\boxed{O(R*r^2*n)}$.

From the \Sequitur paper \cite{sequitur} we
know that the number of rules in the grammar generated by Sequitur
is between $O(\sqrt{n})$ and $O(n)$. Thus the worst case runtime on the similarity
algorithm is $\boxed{O(n^4)}$. This is because we could have up to $r$ replacements.
However, in practice we will see that the runtime is much better
than $O(n^4)$. This is because we found $r$ for our test data to be slightly sublinear
even for complicated english text, and we found that we didn't quite make a linear
number of replacements $R$ with respect to $r$.
so our optimistic runtime could be anywhere 
from $O(n^4)$ to $O(n^{2})$ depending on how $r$ grows.

The inner loops of the Cluster are similar to those of the Similarity algorithm.
We iterate the entire clustering and replacement procedure $C$ times. Going through
each variable-cluster pair takes up to $O(r^2)$ time and calculating the levenshtein
distance takes $O(n)$ time. The time taken to actually perform the replacements each
iteration is absorbed into the $O(r^2)$ term. So, again we have a runtime of
$\boxed{O(C*r^2*n)}$. The big gain over the similarity algorithm is that $C$ turns out
to be nearly constant, since there are very few huge chains of reductions that are
only possible after other reductions have been performed, an in fact we are able to 
perform a very large number of the remaining reductions each time we perform an iteration
of the clustering algorithm. Thus since $C$ is nearly constant, the optimistic runtime
could be anywhere from $O(n^3)$ to $O(n^2)$.

CANT THINK OF PROOF OF NOLOOPS

@@

\begin{verbatim}
Grammar:
~[*] => ~[BC]--~[BC]?

~[AZ] => ~[A]3~[A]~[A] + ~[C]~[C]3~[C]1 = ???
~[A] => 12
~[BC] => ~[AZ]~[AZ]
~[C] => 32
-----------------------
Generated String:
1231212 + 32323321 = ???1231212 + 32323321 = ???--(cont.)
1231212 + 32323321 = ???1231212 + 32323321 = ????
\end{verbatim}

@@

\subsection{Larger Tests}
Genesis-256000
Obfuscated C Code
